---
title: Stream temperatures
author: Charlotte Wickham
output: pdf_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(fig.height = 3)
```

Explore stream temperatures for the sites:

* GSWS01 Andrews Lookout Creek Gaging Station	
* GSMACK Andrews Mack Creek Gaging Station	 
* GSWS01 Andrews Watershed 1 Gaging Station	  	

*This is where we finished last time, but reorganized to group the operations.  I've also added spots for the breakout room activities.*

## Functions

```{r}
# Calculate useful data coverage summaries
coverage_summary <- function(data){
  data %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
}
```


```{r}
# Plot watertemp_day time series
plot_temperature <- function(data, title){
  data %>% 
    ggplot(aes(date, watertemp_mean_day)) + 
    geom_line(aes(color = watertemp_method)) +
    scale_color_brewer("Method", palette = "Set2") +
    labs(x = "", y = "Water temperature (C)",
      title = title)
}
```


## Data Import

```{r, message = FALSE}
streams <- read_csv("data/HT00441_v8.csv")
names(streams) <- tolower(names(streams))
```

Filter to time period of interest, and set observations with anything other than "Accepted" quality to missing:
```{r}
streams <- streams %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

## Site Subsets

```{r}
gslook <- streams %>% 
  filter(sitecode == "GSLOOK")
gsmack <- streams %>% 
  filter(sitecode == "GSMACK")
gsws01 <- streams %>% 
  filter(sitecode == "GSWS01")
```

## Coverage Summaries

```{r}
gslook %>% coverage_summary()
gsmack %>% coverage_summary()
gsws01 %>% coverage_summary()
```

### Breakout Room Activity #1

**Discuss** the following code, e.g. in words what does it do?:
```{r}
streams %>% 
  filter(sitecode %in% c("GSLOOK", "GSMACK","GSWS01")) %>% 
  group_by(sitecode) %>% 
  coverage_summary()
```

**Does it work?** Run it and see.

---

## Plots

```{r}
gslook %>% plot_temperature("GSLOOK")
gsmack %>% plot_temperature("GSMACK")
gsws01 %>% plot_temperature("GSWS01")
```

Take the same approach with plotting:
```{r}

```

### Breakout Room Activity #2

Run the following code and explore `streams_nested`. You might like to look at it on the Console, or using `View()`.

**How does `nest_by()` differ to `group_by()?**

```{r}
streams_nested <- streams %>% 
  nest_by(sitecode) 
```

---

Combine with `rowwise()`:
```{r}

```

Look at a plot:
```{r}

```

