---
title: Stream temperatures
author: Charlotte Wickham
output: pdf_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(fig.height = 3)
```

Explore stream temperatures for the sites:

* GSWS01 Andrews Lookout Creek Gaging Station	
* GSMACK Andrews Mack Creek Gaging Station	 
* GSWS01 Andrews Watershed 1 Gaging Station	  	

*This is where we finished last time*

## Functions

```{r}
# Calculate useful data coverage summaries
coverage_summary <- function(data){
  data %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
}
```


```{r}
# Plot watertemp_day time series
plot_temperature <- function(data, title){
  data %>% 
    ggplot(aes(date, watertemp_mean_day)) + 
    geom_line(aes(color = watertemp_method)) +
    scale_color_brewer("Method", palette = "Set2") +
    labs(x = "", y = "Water temperature (C)",
      title = title)
}
```


## Data Import

```{r, message = FALSE}
streams <- read_csv("data/HT00441_v8.csv")
names(streams) <- tolower(names(streams))
```

Filter to time period of interest, and set observations with anything other than "Accepted" quality to missing:
```{r}
streams <- streams %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

## GSLOOK

Get site data:
```{r}
gslook <- streams %>% 
  filter(sitecode == "GSLOOK")
```

Checks on data quality/coverage:
```{r}
gslook %>% coverage_summary()
```

Plot site stream temperature over time:
```{r}
gslook %>% plot_temperature("GSLOOK")
```

## GSMACK

Get site data:
```{r}
gsmack <- streams %>% 
  filter(sitecode == "GSMACK")
```

Checks on data quality/coverage:
```{r}
gsmack %>% coverage_summary()
```
Plot site stream temperature over time:
```{r}
gsmack %>% plot_temperature("GSMACK")
```

## GSWS01

Get site data:
```{r}
gsws01 <- streams %>% 
  filter(sitecode == "GSWS01")
```

Checks on data quality/coverage:
```{r}
gsws01 %>% coverage_summary()
```

Plot site stream temperature over time:
```{r}
gsws01 %>% plot_temperature("GSWS01")
```


```{r}
streams %>% 
  nest_by(sitecode) 
```

