---
title: Stream temperatures
author: Charlotte Wickham
output: pdf_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(lubridate)
# knitr::opts_chunk$set(fig.height = 3, fig.width = 6)
```

Explore stream temperatures for all sites.

*This is an example of where we might end up*

## Functions

```{r}
# Calculate useful data coverage summaries
coverage_summary <- function(data){
  data %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
}
```


```{r}
# Plot watertemp_day time series
# Note this is the two argument version
plot_temperature <- function(data, title){
  data %>% 
    ggplot(aes(date, watertemp_mean_day)) + 
    geom_line(aes(color = watertemp_method)) +
    scale_color_brewer("Method", palette = "Set2") +
    labs(x = "", y = "Water temperature (C)",
      title = title)
}
```

## Data Import

```{r, message = FALSE}
streams <- read_csv("data/HT00441_v8.csv")
names(streams) <- tolower(names(streams))
```

Filter to time period of interest, and set observations with anything other than "Accepted" quality to missing:
```{r}
streams <- streams %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

## Data coverage

`coverage_summary()` will work on grouped data:
```{r}
streams %>% 
  group_by(sitecode) %>% 
  coverage_summary()
```

## Plots 

One option is to apply the plot to all the data, then
apply facetting to the resulting plot:
```{r}
streams %>% 
  plot_temperature("All sites") +
  facet_wrap(~ sitecode)
```

Alternatively, create and store all the plots with `rowwise()`:
```{r}
streams_with_plots <- streams %>% 
  nest_by(sitecode) %>% 
  rowwise() %>% 
  mutate(plots = list(plot_temperature(data, sitecode)))
```

Display one plot:
```{r}
streams_with_plots$plots[[1]]
```

## Different ways to actually see all the plots

(Also a survey of other iteration methods)

purrrs `walk()` function:
```{r}
streams_with_plots %>% pull(plots) %>% walk(print)
```

dplyrs `group_walk()` function (this both creates and displays the plots):
```{r, eval = FALSE}
streams %>% 
  group_by(sitecode) %>% 
  group_walk(~ print(plot_temperature(.x, .y)))
```

A `for` loop:
```{r, eval = FALSE}
sitecodes <- unique(streams$sitecode)
for (site in sitecodes){
  site_data <- filter(streams, 
    sitecode == site)
  site_data %>% 
    plot_temperature(site) %>% 
    print()
}
```

Or alternatively save plots as PNG files. With purrrs `walk2()`
```{r}
streams_with_plots %>% 
  mutate(
    plot_files = paste0("plots/", sitecode, ".png")
  ) %>% 
  with(walk2(plot_files, plots, ggsave))
```


